Sperm do not evolve to collaborate in female meiotic drive.

### 2014-05-08 writeup_and_notes/male_dependent_drive.tex
added bistable additive figure and code
added male geno. control figure effect_of_dominance_on_invasion_space_four_graph.eps

\section*{Supplementary Stuff}

\begin{figure}
	\rotatebox{90}{
\includegraphics[width = 0.5
          \textwidth]{Scripts/homozyg_bistability.eps}}
\caption{Invasion analysis for a self promoting female meiotic drive allele with
  recessive costs (selection coefficient $s$), showing the region of
  bistability. The colors, and the thin dashed contours, indicate the
  frequency the allele must be above to invade the population (note
  that these alleles reach fixation conditional on invading). In the
  white area the allele can not invade ($x \geq1$), in the solid red
  area the allele can invade and fix when rare. In the left panel we
  show the results obtained by a grid search using the recursion, on
  the right we show the approximation obtained assuming that HWE
  holds. }  
\label{Bistab_homozyg_cost_fig}
\end{figure}

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/bistable_x_vs_d_additive_s.eps} 
\caption{Bistable of a drive allele when selection cost (s) acts
  additively, for an allele whose effect
 on female meoisis is mediated by sperm allele. }  \label{bistable_additive}
\end{figure}

>>>>

\section*{Supplementary Material}

\begin{figure}

\includegraphics[width = 0.5
          \textwidth]{../Scripts/homozyg_bistability.eps}
\caption{Invasion analysis for a self promoting female meiotic drive allele with
  recessive costs (selection coefficient $s$), showing the region of
  bistability. The colors, and the thin dashed contours, indicate the
  frequency the allele must be above to invade the population (note
  that these alleles reach fixation conditional on invading). In the
  white area the allele can not invade ($x \geq1$), in the solid red
  area the allele can invade and fix when rare. In the left panel we
  show the results obtained by a grid search using the recursion, on
  the right we show the approximation obtained assuming that HWE
  holds. }  
\label{Bistab_homozyg_cost_fig}
\end{figure}

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/bistable_x_vs_d_additive_s.eps} 
\caption{The unstable equilibrium frequency for a self promoting
  female meiotic drive allele with an additive cost ($s_h=s/2$) as a
  function of the drive parameter. The solid line shows results
  obtained using the recursion, the dots our approximation given by \eqref{thresh2}/}  \label{bistable_additive}
\end{figure}
